### 2019-04-08 papers/journal/ex-vts.tex
Minor Fixes

The figure~\ref{fig:mukund-vts} represent mammalian SNARE map
created by studying the wide array of literature.
% 
To construct the map, we have assumed that vesicles only contain a
single active v-SNARE, and we have attributed t-SNAREs and inactive
v-SNAREs that travel between compartments to one of the known vesicles
that go between the same source and target compartments.
%
In order to identify the active SNARE complex involved in any
particular vesicle fusion, we used two criteria.
%
The SNARE complex is formed \textit{in vivo}. In most papers, this is
determined by immunoprecipitation of the SNARE complex from the
relevant cell fraction.
%
Blocking SNARE complex formation (for example, using antibodies
against these SNAREs, or using cytosolic forms of these SNAREs) blocks
the specific transport step.
%
Note that these vesicles have been collected from multiple cell types, and
any given cell type is likely to contain only a subset of the vesicles in
the map.

@@

In figure~\ref{fig:yeast-vts}, we present the yeast VTS.
%
We have borrowed the VTS from~\cite{burri2004complete}.
%
It has been adapted from the paper by
separating the v and the t SNAREs. 
%
It is clear that it is an incomplete description of the VTS.
%
For example, the inactive molecules were not reported in the reference.
%
We are currently searching for more literature that can help us complete
all known information about the VTS.
%

>>>>

The Figure~\ref{fig:mukund-vts} represent mammalian SNARE map
created by studying the wide array of literature.
% 
To construct the map, we have assumed that vesicles only contain a
single active v-SNARE, and we have attributed t-SNAREs and inactive
v-SNAREs that travel between compartments to one of the known vesicles
that go between the same source and target compartments.
%
In order to identify the active SNARE complex involved in any
particular vesicle fusion, we used two criteria.
%
The SNARE complex is formed \textit{in vivo}. In most papers, this is
determined by immunoprecipitation of the SNARE complex from the
relevant cell fraction.
%
Blocking SNARE complex formation (for example, using antibodies
against these SNAREs, or using cytosolic forms of these SNAREs) blocks
the specific transport step.
%
Note that these vesicles have been collected from multiple cell types, and
any given cell type is likely to contain only a subset of the vesicles in
the map.

@@

In Figure~\ref{fig:yeast-vts}, we present the yeast VTS.
%
We have borrowed the VTS from~\cite{burri2004complete}.
%
It has been adapted from the paper by
separating the v and the t SNAREs. 
%
It is clear that it is an incomplete description of the VTS.
%
For example, the inactive molecules were not reported in the reference.
%
We are currently searching for more literature that can help us complete
all known information about the VTS.
%

### 2019-04-08 papers/journal/intro.tex
Minor Fixes

\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle, Figure~\ref{fig:vts}.

@@

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\begin{example}
	%
    In figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
    %
    The synthesis is performed against the steady state property and 3-connectivity. 
    %The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for a proper discussion about the nodes and molecules depicted in the diagram). 
    %
    Synthesized edge is in red color and synthesized molecules are presented in blue.
    %
    The synthesis adds one edge and 7 molecules to complete the partial VTS.
    %
    For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.

>>>>

\subsubsection{Vesicle fusion} The process of vesicle fusion involves two steps recognition of the correct target compartment and fusion of the transport vesicle (Figure~\ref{fig:vts}).

@@

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our stability and k-connectivity constraints as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%
\begin{example}
	%
    In Figure~\ref{fig:synth-vts1}, we present a partial input VTS that has 3 compartments. Figure~\ref{fig:synth-vts2} present it's complete output VTS. 
    %
    The synthesis is performed against the steady state property and 3-connectivity. 
    %The tags PM, EE, and LE represent the corresponding nodes (please refer to Appendix~\ref{sec:ex-vts} for a proper discussion about the nodes and molecules depicted in the diagram). 
    %
    Synthesized edge is in red color and synthesized molecules are presented in blue.
    %
    The synthesis adds one edge and 7 molecules to complete the partial VTS.
    %
    For the sake of clarity, we have not presented the activity of molecules, the corresponding pairing matrix and remaining molecules on the nodes.
